---
title: "HW1"
author: "Lowson Li, R08323023"
output:
  html_notebook:
    code_folding: show
    highlight: tango
    number_sections: yes
    theme: simplex
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  html_document:
    df_print: paged
    toc: yes
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: inline
---

```{r message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

# Load packages
```{r}
library(tidyverse)
library(tidygraph)
library(igraph)
library(visNetwork)
```

# Import data
```{r}
library(readr)
class <- read_csv("/Users/leon/Desktop/Social-Network-Analysis/Data/class.csv", col_names = FALSE)
```

# Q1

Generate the network (with 12 nodes) with the given edge set, complete the corresponding analysis and visualization tasks.

Edge set:
1 and 2, 1 and 3, 1 and 4, 1 and 8, 1 and 10, 1 and 11, 1 and 12;
2 and 3, 2 and 4, 2 and 5, 2 and 6;
3 and 5, 3 and 6;
4 and 7, 4 and 9, 4 and 10, 4 and 12;
5 and 9, 5 and 11;
6 and 12;
7 and 11;
8 and 12;
9 and 10;
11 and 12;

1) Report the adjacency matrix, and plot this network with labels.
2) Find the node(s) with maximum degree, what’s the maximum degree value? And find the node(s) with maximum betweenness, what’s the maximum betweenness value?

## Create node list
```{r}
node_list <- tibble(id = 1:12)
```

## Create edge list 
```{r}
edge_list <- tibble(from = c(rep(1, 7), rep(2, 4), rep(3, 2), rep(4, 4), rep(5, 2), 6:9, 11), to = c(2, 3, 4, 8, 10, 11, 12, 3, 4, 5, 6, 5, 6, 7, 9, 10, 12, 9, 11, 12, 11, 12, 10, 12))
```

## Adjancency matrix
```{r}
tbl_graph(nodes = node_list, edges = edge_list, directed = FALSE) %>%
  igraph::get.adjacency()
```


## Plot the networks
### igraph
This will plot original igraph.
```{r}
g <- tbl_graph(nodes = node_list, edges = edge_list, directed = FALSE) # save graph named "g"
g %>%
  plot()
```
### visNetwork
By `visNetwork`, we can plot interactive network.
```{r}
 g %>%
  visIgraph()
```

## Descriptive analysis
### Degree
```{r}
g %>%
  mutate(degree = tidygraph::centrality_degree()) %>%
  arrange(desc(degree))
```
We can found that the node 1 has the maximum degree 7.

### Betweenness

```{r}
g %>%
  mutate(betweenness = tidygraph::centrality_betweenness()) %>%
  arrange(desc(betweenness))
```
We can found that the node 1 has the maximum betweenness 12.7.

# Q2
Import the friendship network in a class represented by an adjacency matrix “class” into R:

1) What is the highest page rank value among nodes?
2) What is the size of the largest component in this network?
3) What is the global clustering coefficient and assortivity of outdegree in this network?
```{r}
# data has imported, change it into igraph networks
g_class <- class %>%
  as.matrix() %>%
  igraph::graph.adjacency(mode = "directed", weighted = NULL)
# though the graph seems undirected, using directed mode will help count outdegree

g_class %>%
  visNetwork::visIgraph()
# use visIgraph function from visNetwork package for interactive view of network
```

## Page rank
```{r}
g_class %>% 
  igraph::page.rank()
```
All of the nodes have the same Page rank scores 0.01886792 since they all point to each other.

## Largest component
```{r}
g_class %>%
  igraph::components() %>%
  .$csize %>%
  sort(decreasing = TRUE)
```
The size of the largest component in this network is 11.

## Global clustering coefficient
```{r}
g_class %>% 
  igraph::transitivity(type = "global")
```
In `igraph`, the global clustering coefficient is call transitivity. The global clustering coefficient of the class network is 1.

## Assortativity of outdegree
```{r}
g_class %>% 
  igraph::assortativity.degree()
```

Since the grapg is symmertric, the ourdegree is qual to the indegree for each node. The assortativity of outdegree is 1.


# References

* [Introduction to Network Analysis with R](https://www.jessesadler.com/post/network-analysis-with-r/)
* [Introducing tidygraph](https://www.data-imaginist.com/2017/introducing-tidygraph/)
* [Introduction to tidygraph & ggraph](https://www.rpubs.com/Steven_Surya/tidygraph-ggraph)
* [Convert a graph to an adjacency matrix or an edge list](http://cneurocvs.rmki.kfki.hu/igraph/doc/R/conversion.html)
* [Tidygraph](http://users.dimi.uniud.it/~massimo.franceschet/ns/syllabus/make/tidygraph/tidygraph.html)
* [visNetwork](https://datastorm-open.github.io/visNetwork/)
* [Social network analysis with R: Descriptive analysis](http://pablobarbera.com/big-data-upf/html/02b-networks-descriptive-analysis.html)
* [Betweenness centrality](https://en.wikipedia.org/wiki/Betweenness_centrality)
* [Import a Matrix as an igraph Network](https://rpubs.com/pjmurphy/310459)
* [Clustering coefficient](https://en.wikipedia.org/wiki/Clustering_coefficient)
* [Assortativity](https://en.wikipedia.org/wiki/Assortativity)