---
title: "HW2"
author: "Lowson Li, R08323023"
output:
  html_notebook:
    code_folding: show
    highlight: tango
    number_sections: yes
    theme: simplex
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  html_document:
    df_print: paged
    toc: yes
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: inline
---

```{r message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

# Load packages
```{r}
library(tidyverse)
library(tidygraph)
library(igraph)
library(spatialreg)
```

# Import data
```{r}
load("../Data/dataset_network_interactions.RData")
str(dataset_lecture3)
```
The data contains 2 lists.
```{r}
dataset_lecture3[[1]] %>% head()
```

The fisrt element of the list contains the adjacency matrix.

```{r}
dataset_lecture3[[2]] %>% head()
```


# Q1
Using the dataset `dataset_network_interactions` provided in the course demonstration, estimate the spatial Durbin model with the regressors WX included. Report your estimation results.


# Q2
Change the specification of weights matrix to binary values, i.e., do not row-standardize the weights matrix, and estimate the above spatial Durbin model again. Report your estimation results.



# References

* [Introduction to Network Analysis with R](https://www.jessesadler.com/post/network-analysis-with-r/)
* [Introducing tidygraph](https://www.data-imaginist.com/2017/introducing-tidygraph/)
* [Introduction to tidygraph & ggraph](https://www.rpubs.com/Steven_Surya/tidygraph-ggraph)
* [Convert a graph to an adjacency matrix or an edge list](http://cneurocvs.rmki.kfki.hu/igraph/doc/R/conversion.html)
* [Tidygraph](http://users.dimi.uniud.it/~massimo.franceschet/ns/syllabus/make/tidygraph/tidygraph.html)
* [visNetwork](https://datastorm-open.github.io/visNetwork/)
* [Social network analysis with R: Descriptive analysis](http://pablobarbera.com/big-data-upf/html/02b-networks-descriptive-analysis.html)
* [Betweenness centrality](https://en.wikipedia.org/wiki/Betweenness_centrality)
* [Import a Matrix as an igraph Network](https://rpubs.com/pjmurphy/310459)
* [Clustering coefficient](https://en.wikipedia.org/wiki/Clustering_coefficient)
* [Assortativity](https://en.wikipedia.org/wiki/Assortativity)