---
title: "HW2"
author: "Lowson Li, R08323023"
output:
  html_notebook:
    code_folding: show
    highlight: tango
    number_sections: yes
    theme: simplex
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  html_document:
    df_print: paged
    toc: yes
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: inline
---

```{r message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

# Load packages
```{r}
library(tidyverse)
library(tidygraph)
library(igraph)
library(visNetwork)
library(spdep)
library(spatialreg)
library(igraph)
library(ade4)
```

# Import data
```{r}
load("../Data/dataset_network_interactions.RData")
str(dataset_lecture3)
```
The data contains 2 lists.
```{r}
dataset_lecture3[[1]] %>% head()
```

The fisrt element of the list contains the variables of students.

```{r}
dataset_lecture3[[2]] %>% head()
```
The second element of the list contains the adjacency matrix

# Q1
Using the dataset `dataset_network_interactions` provided in the course demonstration, estimate the spatial Durbin model with the regressors $W_{x}$ included. Report your estimation results.

## Prepare data

Strategy:
We are using `lagsarlm` (Spatial simultaneous autoregressive model estimation by maximum likelihood) in `spatialreg`.
We need to prepare:

1) The dataframe with variable name 
2) The weighted matrix passed to `listw` argument in `lagsarlm` function
    1) The `nb2listw` function from `spdep` pacakage supplements a neighbours list with spatial weights for the chosen coding scheme. 
    2) It seems like there's no simple way to construct the `nb` object needed for `nb2listw`, we use `neig` function from `ade4` package to convert the edge list to `neig` and use `neig2nb` function from `ade4` package to convert the `neig` to `nb` object.
  
```{r echo=TRUE}
# construct network from adjacency matrix 
network <- igraph::graph.adjacency(dataset_lecture3[[2]],
  mode = c("directed"), weighted = NULL, diag = FALSE
)
```

The network should look like this 
```{r}
network %>% visNetwork::visIgraph(igraph = .)
```


```{r echo=TRUE}
# convert igraph network from edgelist to class nb
# igraph -> neig -> nb
networknb <-
  network %>%
  igraph::get.edgelist() %>%
  ade4::neig(edges = .) %>%
  ade4::neig2nb()
```

This will cause error since some of people are not friends of others.

```{r echo=TRUE}
# randomly assign a friend for those 93 isolated(without any link).
iso <- c(
  4, 9, 26, 31, 33, 34, 36, 49, 54, 61, 62, 69, 73, 75, 77, 81, 83, 84, 88, 89, 95, 96, 100,
  103, 108, 111, 114, 117, 118, 126, 128, 131, 132, 135, 137, 138, 141, 142, 151, 153,
  158, 159, 169, 170, 171, 175, 178, 181, 182, 184, 193, 198, 200, 203, 209, 213, 219,
  221, 223, 231, 242, 244, 246, 248, 249, 251, 252, 253, 255, 257, 259, 267, 269, 272,
  274, 275, 277, 280, 284, 285, 286, 289, 292, 293, 296, 297, 301, 309, 315, 317, 318,
  330, 334
)

set.seed(20200319)

for (i in 1:93) {
  networknb[[iso[i]]] <- sample(1:336, 1)
}
```

```{r echo=TRUE}
# B is the basic binary coding,
# W is row standardised (sums over all links to n),
# C is globally standardised (sums over all links to n),
# U is equal to C divided by the number of neighbours (sums over all links to unity), while S is the variance-stabilizing coding scheme proposed by Tiefelsdorf et al. 1999, p. 167-168 (sums over all links to n).

lw <- spdep::nb2listw(networknb, glist = NULL, style = "W", zero.policy = T)

variable <- data.frame()
variable <- rbind(variable, dataset_lecture3[[1]])
colnames(variable) <- c(
  "gpa", "smoke_freq", "drink", "club", "exer",
  "male", "black", "hisp", "asian", "race_other",
  "both_par", "less_hs", "more_hs", "momedu_miss",
  "Prof", "Home", "job_other"
)
```

## Regression results 

### OLS 
```{r echo=TRUE}
lm(
  gpa ~ male + black + hisp + asian + race_other
  + both_par + less_hs + more_hs
  + momedu_miss + Prof + Home + job_other,
  data = variable
) %>% summary()
```

## SAR
### Default: spatial lag model 
```{r}
lagsarlm(gpa ~ male + black + hisp + asian + race_other
  + both_par + less_hs + more_hs
  + momedu_miss + Prof + Home + job_other,
data = variable, listw = lw, method = "eigen",
quiet = FALSE, zero.policy = TRUE, tol.solve = 1e-13,
type = "lag"
) %>% summary()
```

### Durbin: spatial Durbin model 
```{r}
lagsarlm(gpa ~ male + black + hisp + asian + race_other
  + both_par + less_hs + more_hs
  + momedu_miss + Prof + Home + job_other,
data = variable, listw = lw, method = "eigen",Durbin = TRUE,
quiet = FALSE, zero.policy = TRUE, tol.solve = 1e-13,
type = "lag"
) %>% summary()
```


# Q2
Change the specification of weights matrix to binary values, i.e., do not row-standardize the weights matrix, and estimate the above spatial Durbin model again. Report your estimation results.

## Prepare data 
```{r echo=TRUE}
# Change the specification of weights matrix to binary values

# B is the basic binary coding,
# W is row standardised (sums over all links to n),
# C is globally standardised (sums over all links to n),
# U is equal to C divided by the number of neighbours (sums over all links to unity), while S is the variance-stabilizing coding scheme proposed by Tiefelsdorf et al. 1999, p. 167-168 (sums over all links to n).

lw_b <- spdep::nb2listw(networknb, glist = NULL, style = "B", zero.policy = T)

```

## SAR
### Durbin: spatial Durbin model 
```{r}
lagsarlm(gpa ~ male + black + hisp + asian + race_other
  + both_par + less_hs + more_hs
  + momedu_miss + Prof + Home + job_other,
data = variable, listw = lw_b, method = "eigen",Durbin = TRUE,
quiet = FALSE, zero.policy = TRUE, tol.solve = 1e-13,
type = "lag"
) %>% summary()
```


# References

* [Class nb (spdep) from class igraph](http://r-sig-geo.2731867.n2.nabble.com/Class-nb-spdep-from-class-igraph-td7582350.html)
* [nb2listw](https://www.rdocumentation.org/packages/spdep/versions/1.1-3/topics/nb2listw)
* [Spatial simultaneous autoregressive model estimation by maximum likelihood](https://r-spatial.github.io/spatialreg/reference/ML_models.html#examples)
* [Using igraph for spatial weights as graphs](https://cran.r-project.org/web/packages/spdep/vignettes/nb_igraph.html)
