---
title: "HW4"
author: "Lowson Li, R08323023"
output:
  html_notebook:
    code_folding: show
    highlight: tango
    number_sections: yes
    theme: simplex
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  html_document:
    df_print: paged
    toc: yes
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: inline
---

```{r message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

# Load packages
```{r}
library(tidyverse)
library(knitr)
library(statnet)
library(ergm)
```

# Import data 
```{r}
data(package='ergm')
data(florentine)
```

# Summary data 

## Plot the network
```{r}
plot(flomarriage, main="Florentine Marriage", cex.main=0.8)
```

## Edges & triangles
```{r}
summary(flomarriage ~ edges + triangle)
```


Using the data set `flomarriage` provided in the R package `ergm` to finish the following questions:

# Q1

1. Estimate an ERGM for `flomarriage` network with the specification of **absolute difference in family’s wealth**, the number of edges, and triangles. Report your estimation result.

```{r}
model1 <- ergm(flomarriage ~  absdiff("wealth") + edges + triangle) 
model1 %>% summary()
```

To get a better sense of how less likely it is for a tie to form, we can translate our log-odds into a probability.

```{r}
knitr::kable(plogis(coef(model1)))
```

Model Diagnostics
```{r}
mcmc.diagnostics(model1)
```


# Q2

2. Count separately how many two stars and three stars in the flomarriage network and estimate an ERGM for `flomarriage` network with the specification of the number of edges, two stars and three stars. Report your estimation result.

```{r}
summary(flomarriage ~ kstar(2:3))
```


```{r}
model2 <- ergm(flomarriage ~ edges + kstar(2:3)) 
model2 %>% summary()
```

To get a better sense of how less likely it is for a tie to form, we can translate our log-odds into a probability.

```{r}
knitr::kable(plogis(coef(model2)))
```


Model Diagnostics

```{r}
mcmc.diagnostics(model2)
```


# References

[ergm-terms](https://www.rdocumentation.org/packages/ergm/versions/3.9.4/topics/ergm-terms)

[Exponential Random Graph Modeling](https://rpubs.com/johnsonam007/lab3ERGM)

[Star (graph theory)](https://en.wikipedia.org/wiki/Star_(graph_theory))