---
title: "HW5"
author: "Lowson Li, R08323023"
output:
  html_notebook:
    code_folding: show
    highlight: tango
    number_sections: yes
    theme: simplex
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  html_document:
    df_print: paged
    toc: yes
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: inline
---

```{r message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

# Load packages
```{r echo=TRUE}
library(tidyverse)
library(RSiena)
```

# Import data 
```{r}
?s50
```

## Description 

An excerpt of the network, alcohol consumption, and smoking data for 50 randomly chosen girls from the Teenage Friends and Lifestyle Study data set. Useful as a small example of network and behaviour, for which models can be fitted quickly, and for which there are no missing values.

## Format 

**Adjacency matrix** for the network at **time points 1, 2, 3**; 50 by 3 matrices of alcohol consumption and smoking data for the three time points.


## Glimpse of data 

Data class
```{r}
s501 %>% class
```

First wave data
```{r}
glimpse(s501)
```

Alcohol variables 
```{r}
glimpse(s50a)
```

## Prepare data 
```{r echo=TRUE}
# Now define the objects with the same names as above
# (this step is superfluous if you read the data already).
friend.data.w1 <- s501
friend.data.w2 <- s502
friend.data.w3 <- s503
drink <- s50a
smoke <- s50s
# Dependent variable
?sienaDependent
# First create a 50 * 50 * 3 array composed of the 3 adjacency matrices
friendshipData <- array(c(friend.data.w1, friend.data.w2, friend.data.w3),
  dim = c(50, 50, 3)
)
# and next give this the role of the dependent variable:
friendship <- sienaDependent(friendshipData)

# We also must prepare the objects that will be the explanatory variables.
# Constant actor covariate; smoking for wave 1.
smoke1 <- coCovar( smoke[ , 1 ] )
# Variable actor covariate
alcohol <- varCovar( drink )

# Put the variables together in the data set for analysis
?sienaDataCreate
mydata <- sienaDataCreate( friendship, smoke1, alcohol )
# Check what we have
mydata
```

## Specify the effects
```{r echo=TRUE}
# You can get an outline of the data set with some basic descriptives from
print01Report( mydata, modelname="s50")
# For the model specification we need to create the effects object
myeff <- getEffects( mydata )
# All the effects that are available given the structure
# of this data set can be seen from
effectsDocumentation(myeff)
# For a precise description of all effects, see Chapter 12 in the RSiena manual.
# A basic specification of the structural effects:
?includeEffects
myeff <- includeEffects( myeff, transTrip, cycle3)
# and some covariate effects:
myeff <- includeEffects( myeff, egoX, altX, egoXaltX, interaction1 = "alcohol" )
myeff <- includeEffects( myeff, simX, interaction1 = "smoke1" )
myeff
```

## Algorithm settings 
```{r echo=TRUE}
# Create object with algorithm settings
# Accept defaults but specify name for output file
# (which you may replace by any name you prefer)
?sienaAlgorithmCreate
myalgorithm <- sienaAlgorithmCreate( projname = 's50' )
```

# Estimation
```{r echo=TRUE}
?siena07
ans <- siena07( myalgorithm, data = mydata, effects = myeff)
ans
```

# Check convergence 
```{r}
# For checking convergence, look at the
# 'Overall maximum convergence ratio' mentioned under the parameter estimates.
# It can also be shown by requesting
ans$tconv.max
# If this is less than 0.25, convergence is good.
# If convergence is inadequate, estimate once more,
# using the result obtained as the "previous answer"
# from which estimation continues:
```

# Q1
## 1a
Drop the effect of smoke1 similarity and estimate the model again.
Do this by the function setEffects() using the ``include`` parameter.
Give the changed effects object and the new answer object new names, such as effects1 and ans1, to distinguish them.

```{r}
# check the current effect setting 
myeff
```

Use the similar specification in ``includeEffect()``, and the change the argument ``include = FALSE`` to turn off the effect.
```{r}
effects1 <- setEffect(myeff,simX,interaction1 = "smoke1", include = FALSE)
```

Check the new effect settings.
```{r}
effects1
```

Estimate the new model
```{r echo=TRUE}
ans1 <- siena07( myalgorithm, data = mydata, effects = effects1)
ans1
```

## 1b
Change the three effects of alcohol to the single effect of alcohol similarity, and estimate again.

Check the current effect settings
```{r}
myeff
```

Remove 3 effects of alcohol
```{r echo=TRUE}
effect2 <- setEffect(myeff, egoX,interaction1 = "alcohol",include = FALSE)
effect2 <- setEffect(effect2, altX,interaction1 = "alcohol",include = FALSE)
effect2 <- setEffect(effect2, egoXaltX,interaction1 = "alcohol",include = FALSE)
```

Check the effect setting 
```{r}
effect2
```

Add singel alcohol similarity effect
```{r}
effect2 <- setEffect(effect2, simX, interaction1 = "alcohol", include = TRUE)
```

Check the model 
```{r}
effect2
```

Estimate the new model
```{r echo=TRUE}
ans2 <- siena07( myalgorithm, data = mydata, effects = effects2)
ans2
```

# Q2

## Prepare new data 
```{r echo=TRUE}
# Now we redefine the role of alcohol drinking
# as a dependent behaviour variable.
# Once again, look at the help file
?sienaDependent
# now paying special attention to the <<type>> parameter.
drinking <- sienaDependent( drink, type = "behavior" )

# Put the variables together in the data set for analysis
NBdata <- sienaDataCreate( friendship, smoke1, drinking )
NBdata
NBeff <- getEffects( NBdata )
effectsDocumentation(NBeff)
NBeff <- includeEffects( NBeff, transTrip, transRecTrip )
NBeff <- includeEffects( NBeff, egoX, altX, egoXaltX,
                         interaction1 = "drinking" )
NBeff <- includeEffects( NBeff, simX, interaction1 = "smoke1" )
NBeff
# For including effects also for the dependent behaviour variable, see
?includeEffects
NBeff <- includeEffects( NBeff, avAlt, name="drinking",
                         interaction1 = "friendship" )
NBeff

# To increase efficiency, we adjust the algoritm 
myalgorithm1 <- sienaAlgorithmCreate( projname = 's50', doubleAveraging=0)

# Estimate again, using the second algorithm right from the start.
NBans <- siena07( myalgorithm1, data = NBdata, effects = NBeff)
# You may improve convergence (considering the overall maximum
# convergence ratio) by repeated estimation in the same way as above.

# Look at results
NBans
# Make a nicer listing of the results
siena.table(NBans, type="html", sig=TRUE)
# This produces an html file; siena.table can also produce a LaTeX file.
```


## 2a
Replace the average alter effect by average similarity (avSim) or total similarity (totSim) and estimate the model again.

Check the currenct effect setting 
```{r}
NBeff
```


Change the effect setting
```{r echo=TRUE}
NBeff1 <- includeEffects(NBeff, avAlt,
  name = "drinking",
  interaction1 = "friendship", include = FALSE
)

NBeff1 <- includeEffects(NBeff1, avSim,
  name = "drinking",
  interaction1 = "friendship", include = TRUE
)
```

Estimate the new model 
```{r echo=TRUE}
NBans1 <- siena07( myalgorithm1, data = NBdata, effects = NBeff1)
NBans1
```

## 2b
Add the effect of smoking on drinking and estimate again.

Check the available effects
```{r}
effectsDocumentation(NBeff1)
```

Include **effect smoke1 on rate drinking**
```{r}
NBeff2 <- setEffect(NBeff1, RateX, name = "drinking", interaction1 = "smoke1", type = "rate")
```

Estimate the new model 
```{r echo=TRUE}
NBans2 <- siena07( myalgorithm1, data = NBdata, effects = NBeff2)
NBans2
```

OPTIONAL: If estimation results should show insufficient convergence (i.e., the convergence t-ratios are not all between -0.1 and +0.1 for the estimated(!) parameters, and the overall maximum convergence ratio is below .25), another run with better starting values may help. The option ‘prevAns’ makes it possible to use the last available estimates as starting values for a new run:

```{r echo=TRUE}
NBans2 <- siena07(myalgorithm1,
    data = NBdata,
    effects = NBeff2,
    verbose = FALSE,
    returnDeps = TRUE,
    prevAns = NBans2)

NBans2
```



# References

[RSiena Manual](http://www.stats.ox.ac.uk/~snijders/siena/RSiena_Manual.pdf)

[RSiena Workshop - Network Evolution](http://steglich.gmw.rug.nl/workshops/network-dynamicsMarkdown.html#(5)_model_estimation)